Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-05-24 edubots_surveys.Rnw
Supress messages
Completing Introduction with preliminary work

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected community. 
% Antonio - En realidad, la comunidad afectada incluiría también a los estudiates, ¿no?
% Por cierto, quizá también se podrían incluir aqui las encuestas pasadas a los estudiantes. No son las mismas preguntas, pero van en una línea similar. Quizá tuviesen cabida y le darían 
% más enjundia al estudio. ;)
% They are not part of this paper, Antonio. Also: write in English - JJ
In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think about the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable. We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching. Our conclusions might help with the adoption of messaging platforms, as well as chatbots or other kind of bots, by higher education institution, and how these must be introduced to teachers so that it helps them achieve desired educational outcomes.
\end{abstract}

@@

<<setup, echo=FALSE>>=
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(ggthemes)

@@

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, 
% customized en lugar de personalized? Por no repetir personalized dos veces en la misma frase
adapting individuals' pace of learning, who get personalized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.

@@

% Maybe move it to a different place later
Given the potential advantages that chatbots could bring to the classroom, as a previous step, we have performed a survey to 300 teachers asking about their attitudes towards the use of chatbots in their classes. We analyse in this work their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes?? }
\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }

>>>>

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and chatbots attached to it, in higher education, requires careful consideration of all options, but above all, an examination of the attitudes of the affected teaching community. 
In this paper we have surveyed the opinions of tertiary education teachers based mainly in Spain and Spanish speaking countries, looking at what they think about the introduction of messaging platforms and chatbots, what their needs are, what kind of use cases they see for them, and in what kind of environment they think its use will be valuable. We will examine how and when these attitudes vary across gender, experience, and other factors, such as the kind of discipline they are teaching. Our conclusions might help with the adoption of messaging platforms, as well as chatbots or other kind of bots, by higher education institution, and how these must be introduced to teachers so that it helps them achieve desired educational outcomes.
\end{abstract}

@@

<<setup, echo=FALSE,message=FALSE>>=
library(ggplot2)
library(dplyr)
library(tidyr)
library(scales)
library(ggthemes)

@@

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, 
% Antonio - customized instead personalized? we are repeating 'personalized' twice in a sentence...
adapting individuals' pace of learning, who get personalized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.

@@

Given the potential advantages that chatbots could bring to the classroom, as a previous step, we created two surveys for bachelor and master degree students at the University of Granada (Spain), which were answered by more than 250 pupils. The obtained results were analysed in \cite{MoraChatbos2021} aiming to identify students' actual needs. The survey asked about their preferences on tools/applications for chatting and messaging, how do they use them in the educational context, who do they like to be in the class messaging groups, and what do they expect bots and chatbots to do to aid them for learning. The conclusions show that students prefer to use known messaging applications, such as Telegram or WhatsApp, mainly to communicate in groups including both classmates and teachers, and they expect chatbots to ease their subject organisation, such as calendar bots, as well as bots to provide grades and subject material.

% Maybe move it to a different place later
In the present work we aim to complement this study with the other main community of the educational process, i.e. teachers. Thus, we have performed a survey among 300 teachers asking about their attitudes towards the use of bots or chatbots in their classes. We analyse their responses, since we are interested in discussing implications and the impact for the development of future technology-enhanced tools and the Education institutions policies regarding the following research questions:
\begin{itemize}
\item{ RQ1 - Are teachers already using messaging apps in their classes? } %This was the second survey, not the  first survey. I wonder if maybe we could invert the presentation order - JJ
\item{ RQ2 - Which kind of chatbots would teachers find useful in their classes?? }
\item{ RQ3 - Which kind of interaction do teachers prefer with their students? }
